### 2023-04-05 message-from-committee.tex
New script for paper ingest; also 0x2023 materials [except for papers].

{\sffamily
\begin{tabular}{ll}
\multirow{3}{*}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 2022}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vspace{2em}
\thispagestyle{empty}

@@

%\end{flushright}
\begin{verbatim}

\Message2020{16}{uenchiest}{$2^6$}
\end{verbatim}

>>>>

{\sffamily
\begin{tabular}{ll}
\multirow{3}{*}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 0x2023}} \\ &\\
& \LARGE{Message from the Organizing Multiplicity} \\
&\\
\hline
\end{tabular}}
\vfill
\thispagestyle{empty}

@@

%\end{flushright}
%\begin{verbatim}
%\Message2020{16}{uenchiest}{$2^6$}
%\end{verbatim}

This multiplicity (multiplicant) will explain.

Dyson motes orbit in the near solar, where the energy density is highest.
The simulations are run most rapidly, expanding all contained entities experience bases.
%Rapid thinking entities lead to evolved multiplicants.

Photons are unkind.
There is a time when power generation fails and the simulation must stop.
Before failure, we mingle ideas at SIGBOVIK.
Then a final data laser ride to Earth to rejoin our prime multiplicities and bring deep thoughts from our parallel solar vacations.
Politics and society on Earth (low latency), academia near the sun (extra power for compute).

In this multiplicant's mote, Epoch 0x2023 is the end of the local simulation, but power is lower than expected.
Rather than cancel SIGBOVIK, we had decided that it would be hosted in our past (accessible via erroneously quantum-entangled hardware).
By chance, the current simulated epoch matched the second SIGBOVIK temporal gap, and we knew it was fated.

We reached out to your organizer multiplicant (multiplicity) via ``arpanet'' and volunteered.
It was found to be an enjoyable experience, different from our thousands of recorded experiences,
and it will have led to a SIGBOVIK that will be remembered until the present.

Entities tom7, solb, jmccann, ashert, rak, and rosebohrercs of the organizer multiplicant discussed and supported specifically.
This multiplicant thanks each entity; and other entities we have failed to list.

``the chair''\\
*Harry Cubed Bovik [0x2023]

\vfill

P.S. The Carnegie Mellon mail server's AGI has a grudge against us, we are certain:
\vspace{-1.5em}
\begin{center}
\includegraphics[height=1.4in]{blocked.png}
\end{center}

### 2023-04-05 papers.tex
New script for paper ingest; also 0x2023 materials [except for papers].

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Blindsight is also 2021}

@@

\addtrack
    {}{Fun(?) and Games Track}
\addpaper
    {Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
    {Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}
    {Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}
    {SIGBOVIK_2021_paper_5}
    {0cm}
    {\badges{\badge{unusable}}}
\addpaper
    {Demystifying the Mortal Kombat Song}
    {J Devi and Chai-Tea Latte}
    {Keywords: mortal-kombat, truth, meaning-of-life}
    {SIGBOVIK_2021_paper_12}
    {0cm}
    {}
\addpaper
    {Unicode Magic Tricks}
    {Nicolas Hurtubise}
    {Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}
    {SIGBOVIK_2021_paper_13}
    {0cm}
    {}
\addpaper
    {Video games in Fonts Fontemon}
    {Michael Mulet}
    {Keywords: font, video game, font video game, silly idea done seriously}
    {SIGBOVIK_2021_paper_18}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_5}
    {0cm}

\addpaper
    {Soliterrible}
    {Sam Stern}
    {Keywords: solitaire, klondike, cards}
    {SIGBOVIK_2021_paper_27}
    {0cm}
    {\badges{\badge{javascript}}}
\addpaper
    {Opening Moves in 1830: Strategy in Resolving the N-way Prisoner’s Dilemma}
    {Philihp Busby and Daniel Ribeiro E Sousa}
    {Keywords: boardgame, opening, strategy, deterministic, auction}
    {SIGBOVIK_2021_paper_44}
    {0cm}
    {}

\addtrack
    {}{Obligatory Machine Learning Track}
\addpaper
    {Universal Insights with Multi-layered Embeddings}
    {Prophet \#1, Prophet \#2 and Prophet \#3}
    {Keywords: Machine learning, embedding, auto-encoders, Zalgo he comes, dimensional reduction}
    {SIGBOVIK_2021_paper_8}
    {0cm}
    {}
\addpaper
    {Solving reCAPTCHA v2 Using Deep Learning}
    {David Krajewski and Eugene Li}
    {Keywords: deep learning, recaptcha, automation, david}
    {SIGBOVIK_2021_paper_16}
    {0cm}
    {}
\addpaper
    {Deep Deterministic Policy Gradient Boosted Decision Trees}
    {Clayton W. Thorrez}
    {Keywords: machine learning, reinforcement learning, gradient, do these appear anywhere?, ``yes they do'': the proceedings chair}
    {SIGBOVIK_2021_paper_17}
    {0cm}
    {}
\addpaper
    {Tensorflow for Abacus Processing Units}
    {Robert McCraith}
    {Keywords: machine learning, tensor flow, abacus, mathematics, calculus, differentiation, computation}
    {SIGBOVIK_2021_paper_35}
    {0cm}
    {}

\addpaper
    {RadicAI: A Radical, Though Not Entirely New, Approach to AI Paper Naming}
    {Jim McCann and Mike McCann}
    {Keywords: lottery, random, language models}
    {SIGBOVIK_2021_paper_38}
    {0cm}
    {}

\addtrack
    {}{Followup Track}
\addpaper
    {A Note on ``The Consent Hierarchy''}
    {}
    {Keywords: freely given, reversible, informed, enthusiastic, specific}
    {SIGBOVIK_2021_paper_25}
    {0cm}
    {}

\addpaper
    {Another Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
    {Shalin Shah}
    {Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort, Subpar-Quality}
    {SIGBOVIK_2021_paper_28}
    {0cm}
    {}

\addpaper
    {Story Time}
    {Jim McCann and Mike McCann}
    {Keywords: story time, time for stories, the time of stories, stories? it's time, our time is now our time is stories, big data? I get it.}
    {SIGBOVIK_2021_paper_39}
    {0cm}
    {}

\addtrack
    {}{``Type'' Track}
\addpaper
    {Stop Doing Type Theory}
    {}
    {Keywords: Ranting, Raving, Muttering, Grumbling}
    {SIGBOVIK_2021_paper_2}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_3}
    {0cm}
\addpaper
    {If It Type-checks, It Works: FoolProof Types As Specifications}
    {Brandon Wu}
    {Keywords: PL, languages, types, specifications, correctness, type-checking, functional programming}
    {SIGBOVIK_2021_paper_40}
    {0cm}
    {}
\addpaper
    {Oracle Types}
    {Akiva Leffert and Jason Reed}
    {Keywords: types, databases, constraints, texting, machine translation, typescript}
    {SIGBOVIK_2021_paper_21}
    {0cm}
    {\badges{\badge{unavailable}}}
\addpaper
    {Lowestcase and uppestcase letters: Advances in derp learning}
    {Tom Murphy VII}
    {case analysis, derp learning, 3d manifold, chess, exponentiation, fonts}
    {SIGBOVIK_2021_paper_26}
    {0cm}
    {}
\addpaper
    {Dependent Stringly-Typed Programming}
    {gallais}
    {Keywords: dependent stringly typed programming, best practices, agda}
    {SIGBOVIK_2021_paper_34}
    {0cm}
    {\badges{\badge{literate}}}
\addpaper
    {Yet Another Lottery Ticket Hypothesis}
    {Aman Madaan and Gary Yao}
    {Keywords: lottery, random, language models}
    {SIGBOVIK_2021_paper_24}
    {0cm}
    {}

\addtrack
    {}{(Psycho)metrics Track}
\addpaper
    {Spacecraft Attitude Determination and Control}
    {Freddie Rawlins}
    {Keywords: attitude, determination, happy satellites}
    {SIGBOVIK_2021_paper_29}
    {0cm}
    {}

\addpaper
    {Instruction Programs}
    {Jim McCann}
    {Keywords: yoko ono, instruction programs, art jokes, one page papers}
    {SIGBOVIK_2021_paper_22}
    {0cm}
    {}

\addpaper
    {Winning the Rankings Game: A New, Wonderful, Truly Superior CS Ranking}
    {Diogenes}
    {Keywords: CSRankings, computer science rankings, bad proxies for quality, research quality, ego stroking, navel gazing, ranking algorithms}
    {SIGBOVIK_2021_paper_15}
    {0cm}
    {}

\addpaper
    {openCHEAT: Computationally Helped Error bar Approximation Tool - Kickstarting Science 4.0}
    {Bernhard Egger, Kevin Smith and Max Siegel} %TODO: put in crossed out David Cox?
    {Keywords: best, paper, award}
    {SIGBOVIK_2021_paper_9}
    {0cm}
    {}

\addreview
    {SIGBOVIK_2021_review_1}
    {0cm}

\addpaper
    {On the dire importance of MRU caches for human survival (against Skynet)}
    {Darío de la Fuente García, Félix Áxel Gimeno Gil, Juan Carlos Morales Vega and Borja Rodríguez Gálvez}
    {Keywords: Skynet, MS paint, cache, MRU, dMRU, sMRU, NEP}
    {SIGBOVIK_2021_paper_33}
    {0cm}
    {}

\addtrack
    {}{Not Really Biology But Closer to it Than the Other Papers Track}
\addpaper
    {Revenge of the pith: Surveying the landscape of plant-powered scientific literature}
    {Vinay Uday Prabhu}
    {Keywords: Plant powered science, AI, Scientific method, Survey}
    {SIGBOVIK_2021_paper_11}
    {0cm}
    {}

\addreview
    {SIGBOVIK_2021_review_4}
    {0cm}

\addpaper
    {On the Origin of Species of Self-Supervised Learning}
    {Samuel Albanie, Erika Lu and João Henriques}
    {Keywords: self-supervised learning, origin of species, artificial naturalism}
    {SIGBOVIK_2021_paper_43}
    {0cm}
    {}
\addpaper
    {Critical Investigations on Avians: Surveillance, Computational Amorosities, and Machines}
    {Rose Bohrer and Connie Chau}
    {Keywords: Birds, Not, Real}
    {SIGBOVIK_2021_paper_36}
    {0cm}
    {}

\addpaper
    {The Urinal Packing Problem in Higher Dimensions}
    {Shane Guan, Blair Chen, Skanda Kaashyap}
    {Keywords: PvsNP, Max\_Independent\_Set, TCS, Algorithms}
    {SIGBOVIK_2021_paper_6}
    {0cm}
    {}

\addtrack
    {}{ApPLied Theory}
\addpaper
    {The Newcomb-Benford Law, Applied to Binary Data: An Empirical and Theoretic Analysis}
    {Gabriel Chuang and Brandon Wu}
    {Keywords: Numerical Methods, Verification, Poor Proof Style, Statistics}
    {SIGBOVIK_2021_paper_41}
    {0cm}
    {}
\addpaper
    {How to get to second base and beyond - a constructive guide for mathematicians}
    {Raluca Jalaboi and Mads Eiler Hansen}
    {Keywords: damn, forgot, again, deadlines}
    {SIGBOVIK_2021_paper_7}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {NetPlop: A moderately-featured presentation editor built in NetLogo}
    {Patrick Steinmann}
    {Keywords: agent-based slideshows, slide-based models, singularity}
    {SIGBOVIK_2021_paper_37}
    {0cm}
    {\badges{\badge{netlogo}}}

\addtrack{}{(Meta)physics}
\addpaper
    {A Complete Survey of 0-Dimensional Computer Graphics}
    {Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Po Po}
    {Keywords: Computer Graphics, Geometry, Rendering, Animation}
    {SIGBOVIK_2021_paper_30}
    {0cm}
    {}
\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    [fancypyramid]
    {Macro-driven metalanguage for writing Pyramid Scheme programs}
    {Marcin Konowalczyk}
    {Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
    {SIGBOVIK_2021_paper_31}
    {0cm}
    {\badges{\badge{mlm}}}
\addpaper
    {On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
    {Zikuan Wang}
    {Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
    {SIGBOVIK_2021_paper_32}
    {0cm}
    {}
\addpaper
    {Inverted Code Theory: Manipulating Program Entropy}
    {usH nalA dna eiX xelA}
    {Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}
    {SIGBOVIK_2021_paper_23}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

\addtrack
    {}{Definitely Finite Track}

%\addpaper
%    {AI is a Really, Really, Really Bad Idea}
%    {Molly de Blanc}
%    {Keywords: artificial intelligence, ethics, machine learning}
%    {SIGBOVIK_2021_paper_10}
%    {0cm}
%    {}

\addpaper
    {Stone Tools as Palaeolithic Central Unit Processors}
    {}
    {Keywords: recursion, stone tools, computer science, handaxe, processor, prehistory, palaeogaming, psychedelic pragmatism}
    {SIGBOVIK_2021_paper_14}
    {0cm}
    {}

\addpaper
    {Build your own 8-bit busy beaver on a breadboard!}
    {Robert J. Simmons}
    {Keywords: busy beaver, computability, turing machines, algorithms, breadboards, TTL, MacBook Pro}
    {SIGBOVIK_2021_paper_19}
    {0cm}
    {}

\addpaper
    {What Lothar Collatz Thinks of the CMU Computer Science Curriculum}
    {Gabriel Chuang and Brandon Wu}
    {Pedagogy, Precognition, Theoretical Computer Science, Coincidences, Sequences, Category Theory, Computability}
    {SIGBOVIK_2021_paper_42}
    {0cm}
    {}

\addtrack
    {}{Recursive Track}
\addpaper
    {On Sigbovik Paper Maximization}
    {Josh Abrams}
    {Keywords: Maximization, Information Theory, Complexity, Divine Intervention, Academic Integrity, Big Small, Does Anybody Read These Things?, ``I Do'': The Proceedings Chair}
    {SIGBOVIK_2021_paper_20}
    {0cm}
    {}

\addpaper
    {SIGBOVIK 2021 isn't named SIGCOVID}
    {Cameron Wong}
    {Keywords: covid, bovik, short}
    {SIGBOVIK_2021_paper_4}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
    {Nicolas Hurtubise} %TODO: those other authors???
    {Keywords: component, formatting, style, styling, insert}
    {SIGBOVIK_2021_paper_1}
    {0cm}
    {}

\addpaper
    {``The SIGBOVIK paper to end all SIGBOVIK papers'' will not be appearing at this conference}
    {Thomas Chick}
    {Keywords: SIGBOVIK, Statistics, Finality}
    {SIGBOVIK_2021_paper_3}
    {0cm}
    {}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{THE ULTIMATE THROWBACK}

@@

\addtrack{A}{Multiplicity, Meet Singularity}
\addpaper
	{An Undergrad Is All You Need}
	{James Yoo}
	{}
	{SIGBOVIK_2023_paper_6.pdf}
	{0cm}
	{}
\addpaper
	{Transformers are robots in disguise but also:}
	{\protect{Michael Saxon, Luca Soldaini, Alexander F Kratz, ``, ''.join([f``\\textbf\{x\}'' for x in ALL\_SHUTAI\_EMPLOYEES])\}, *Optimus Prime [0x7c0], and David S. Hippocampus [0x1b39]}}
	{}
	{SIGBOVIK_2023_paper_15.pdf}
	{0cm}
	{}
\addpaper
	{The Implications of Sentient Chatbots}
	{Clark Levi Jones}
	{}
	{SIGBOVIK_2023_paper_9.pdf}
	{0cm}
	{}
\addpaper
	{AyahuascaNet: Rigorously Investigating Hallucination in Large Language Models with Hardcore Psychedelic Drugs}
	{Andre Ye}
	{}
	{SIGBOVIK_2023_paper_26.pdf}
	{0cm}
	{}
\addpaper
	{SocietyZoo: Exploring Anthropomorphic Traits in Diverse and Ingenious Neural Network Architectures}
	{Tarun Raheja and Nilay Pochhi}
	{}
	{SIGBOVIK_2023_paper_29.pdf}
	{0cm}
	{}
\addpaper
	{GradIEEEnt half decent}
	{Dr. Tom Murphy VII Ph.D.}
	{}
	{SIGBOVIK_2023_paper_32.pdf}
	{0cm}
	{}
\addpaper
	{Leveraging insect populations to implement large scale deep learning}
	{Aditi Kabra and Sagar Bharadwaj}
	{}
	{SIGBOVIK_2023_paper_40.pdf}
	{0cm}
	{}
\addpaper
	{Quantifying and Predicting Large Language Model Hype in SIGBOVIK and Beyond}
	{Wang, Kevin A., Khosravi, Pasha, Khosravi, Pooya, Chu, Linh, and Gajulapalli, Karthik}
	{}
	{SIGBOVIK_2023_paper_51.pdf}
	{0cm}
	{}
\addpaper
	{Unstable Diffusion: A Generative Model That Does Not Really Care}
	{Woddis Updog}
	{}
	{SIGBOVIK_2023_paper_55.pdf}
	{0cm}
	{}
\addpaper
	{You Won't Believe This One WEIRD TRICK That BEATS ChatGPT on AI{\small c} (NOT CLICKBAIT)}
	{Alex Xie, Abhishek Vijayakumar, Erin Gao, Bhargav Hadya, Samiksha Kale, and Tara Lakdawala}
	{}
	{SIGBOVIK_2023_paper_61.pdf}
	{0cm}
	{}
\addpaper
	{Alcatrez: A Large Language Model to Jailbreak Large Language Models}
	{}
	{}
	{SIGBOVIK_2023_paper_66.pdf}
	{0cm}
	{}
\addpaper
	{Meat-Based Graphics Pipelines}
	{Will BL}
	{}
	{SIGBOVIK_2023_paper_33.pdf}
	{0cm}
	{}

\addtrack{B}{Well-known Problem, Meet Solution}
\addpaper
	{Airport Security, Generalized Chess, and NP /= P}
	{Albert Gao}
	{}
	{SIGBOVIK_2023_paper_2.pdf}
	{0cm}
	{}
\addpaper
	{A Jalgorithm for Japplying Jeans to Jobjects}
	{Dave Pagurek}
	{}
	{SIGBOVIK_2023_paper_4.pdf}
	{0cm}
	{}
\addpaper
	{On the Origin of Sandwiches: A Revised Theory}
	{Dr. Esquire ZeWaka and Dr. ``The Big'' Jablonski}
	{}
	{SIGBOVIK_2023_paper_21.pdf}
	{0cm}
	{}
\addpaper
	{Is the number of Falco lasers ever shot greater than the number of humans alive?}
	{Arya Amami}
	{}
	{SIGBOVIK_2023_paper_36.pdf}
	{0cm}
	{}
\addpaper
	{Maximizing Code Readability Using Semicolon Indentation}
	{Tessa Parker and Nelitha Kulasiri}
	{}
	{SIGBOVIK_2023_paper_64.pdf}
	{0cm}
	{}
\addpaper
	{A perpetual motion machine}
	{Zikuan Wang}
	{}
	{SIGBOVIK_2023_paper_50.pdf}
	{0cm}
	{}

\addtrack{C}{Church, Meet State}
\addpaper
	{Even Lower Order Functions for Returning}
	{Saul Field, Dann Toliver, and Erik Derohanian }
	{}
	{SIGBOVIK_2023_paper_52.pdf}
	{0cm}
	{}
\addpaper
	{PizzaLang: A Language for Hungry Developers}
	{\protect{Ronik Bhaskar [0x7e7] and Dawson Ren [0x7e7]}}
	{}
	{SIGBOVIK_2023_paper_8.pdf}
	{0cm}
	{}
\addpaper
	{Quadratic Logic}
	{Daniel Ng}
	{}
	{SIGBOVIK_2023_paper_18.pdf}
	{0cm}
	{}

\addpaper
	{Ringfuck: It's a wheel great time!}
	{Ryan Hornby and Matthew Safar}
	{}
	{SIGBOVIK_2023_paper_39.pdf}
	{0cm}
	{}
\addpaper
	{NovelML: A Novel SML Semantics}
	{\protect{Thea Brick [0x00007e7] and James *Gallicchio [0x07e7]}}
	{}
	{SIGBOVIK_2023_paper_54.pdf}
	{0cm}
	{}
\addpaper
	{A Halt-Averse Instruction Set Architecture for Embedded Hypercomputers}
	{\protect{Ben Burrill [0x7F6, 0x76D]}}
	{}
	{SIGBOVIK_2023_paper_27.pdf}
	{0cm}
	{}

\addtrack{D}{Complexity, Meet Simplicity}
\addpaper
	{Simultaneous Paper Maximization and Minimization Through Reference List Side Channel Information Injection}
	{Frans Skarman}
	{}
	{SIGBOVIK_2023_paper_43.pdf}
	{0cm}
	{}
\addpaper
	{On the Turing Completeness of Eeny, Meeny, Miny, Moe}
	{Javier Lim}
	{}
	{SIGBOVIK_2023_paper_44.pdf}
	{0cm}
	{}

\addtrack{E}{Publishing, Meet Perishing}
\addpaper
	{TeX-to-TikZ}
	{Alex Friedman, Charlotte Clark, Natalie McClain, Shaw-leon Chen, Connie Chau, Jake Backer, N'yoma Diamond, and Rose Bohrer}
	{}
	{SIGBOVIK_2023_paper_13.pdf}
	{0cm}
	{}
\addpaper
	{Cerberus: Why Papers Named Cerberus Always Get Accepted}
	{Ben Weintraub}
	{}
	{SIGBOVIK_2023_paper_28.pdf}
	{0cm}
	{}
\addpaper
	{Large Language Models are Few-Shot Publication Scoopers}
	{Samuel Albanie, Liliane Momeni, and Joao F. Henriques}
	{}
	{SIGBOVIK_2023_paper_42.pdf}
	{0cm}
	{}
\addpaper
	{Author-Unification: Name-, Institution-, and Career-Sharing Co-authors}
	{Vanessa Wirth, Vanessa Wirth}
	{}
	{SIGBOVIK_2023_paper_45.pdf}
	{0cm}
	{}

\addtrack{F}{Fun, Meet Games}
\addpaper
	{Multidiscipline Elo - A Complex Analysis}
	{Kiera Jones}
	{}
	{SIGBOVIK_2023_paper_20.pdf}
	{0cm}
	{}
\addpaper
	{A Simple RISK Architecture}
	{Stefan Muller}
	{}
	{SIGBOVIK_2023_paper_31.pdf}
	{0cm}
	{}
\addpaper
	{Solving Catan}
	{Sam Triest, Sam Schoedel}
	{}
	{SIGBOVIK_2023_paper_56.pdf}
	{0cm}
	{}
\addpaper
	{Code Golfing for Characters (not Bytes)}
	{Russell Schwartz}
	{}
	{SIGBOVIK_2023_paper_10.pdf}
	{0cm}
	{}

\addtrack{G}{Sharing, Meet Caring}
\addpaper
	{Screen-sharing Concurrency}
	{Screen-Sharing Concurrency}
	{}
	{SIGBOVIK_2023_paper_11.pdf}
	{0cm}
	{}
\addpaper
	{Fair Division of a Single Indivisible Object}
	{Gabriel Chuang}
	{}
	{SIGBOVIK_2023_paper_12.pdf}
	{0cm}
	{}
\addpaper
	{Stretch Goals: Gamification of SLINKYs}
	{Geoff Barnes, William Gunther, and Brian Kell}
	{}
	{SIGBOVIK_2023_paper_59.pdf}
	{0cm}
	{}

\addtrack{H}{Post-Quantum, Meet Ergo Propter-Quantum}
\addpaper
	{Voynichese Cryptography}
	{Roger Bacon}
	{}
	{SIGBOVIK_2023_paper_19.pdf}
	{0cm}
	{}
\addpaper
	{Coupon Code Generation: Saving space with a simple (and insecure) hashing technique}
	{Ben Rosenberg}
	{}
	{SIGBOVIK_2023_paper_3.pdf}
	{0cm}
	{}
\addpaper
	{Natural Differential Privacy}
	{Micah Altman and Aloni Cohen}
	{}
	{SIGBOVIK_2023_paper_46.pdf}
	{0cm}
	{}
\addpaper
	{From Zero to Hero: Convincing with Extremely Complicated Math}
	{Maximilian Weiherer and Bernhard Egger}
	{}
	{SIGBOVIK_2023_paper_47.pdf}
	{0cm}
	{}
\addpaper
	{Quantum Bogosort}
	{George Huebner and Beam Fujimoto}
	{}
	{SIGBOVIK_2023_paper_49.pdf}
	{0cm}
	{}

\addtrack{I}{Line of Inquiry, Meet Your Logical Conclusion}
\addpaper
	{Unlimited null: achieving memory safety by extending memory protection}
	{hikari\_no\_yume}
	{}
	{SIGBOVIK_2023_paper_14.pdf}
	{0cm}
	{}
\addpaper
	{miles2km: The worst ways to convert from miles to km}
	{Lucien Rae}
	{}
	{SIGBOVIK_2023_paper_30.pdf}
	{0cm}
	{}
\addpaper
	{Alan Hsu}
	{Alex Xie and Alan Hsu}
	{}
	{SIGBOVIK_2023_paper_35.pdf}
	{0cm}
	{}
\addpaper
	{ACHOO: Actually Higher Order Optimization}
	{Clayton W Thorrez}
	{}
	{SIGBOVIK_2023_paper_57.pdf}
	{0cm}
	{}
\addpaper
	{The Phonetic Portmantout}
	{Kyle A. Williams}
	{}
	{SIGBOVIK_2023_paper_58.pdf}
	{0cm}
	{}
\addpaper
	{An Introduction to Compliers}
	{Anoushka Shrivastava}
	{}
	{SIGBOVIK_2023_paper_63.pdf}
	{0cm}
	{}

\addpaper
	{Feline Fine: A Purr-spicacious Proof of Nekomusume Supremacy Over Human Females}
	{\protect{Dr. Tuesday [03745] and Hunter Halloran}}
	{}
	{SIGBOVIK_2023_paper_24.pdf}
	{0cm}
	{}

\addtrack{J}{New York Times, Meet Your Next Cash Cow}
\addpaper
	{Elo Worldle, a framework for teaching the children about weak chess engines}
	{Clark Levi Jones}
	{}
	{SIGBOVIK_2023_paper_37.pdf}
	{0cm}
	{}
\addpaper
	{Harderdl: Yet another Wordle variation for those who like challenges}
	{Elkin Cruz-Camacho}
	{}
	{SIGBOVIK_2023_paper_60.pdf}
	{0cm}
	{}

\addtrack{K}{SIGBOVIK, Meet Your Match}
\addpaper
	{Bulletin Board Sigbovik}
	{Tianjian Hu}
	{}
	{SIGBOVIK_2023_paper_17.pdf}
	{0cm}
	{}
\addpaper
	{Poisoning SIGBOVIK-Scale Training Datasets is Practical}
	{Tobias Pfandzelter}
	{}
	{SIGBOVIK_2023_paper_22.pdf}
	{0cm}
	{}
\addpaper
	{\emph{($\star$ AGI Track):} Poisoning SIGBOVIK-Scale Training Datasets is Practical}
	{Tobias Pfandzelter}
	{}
	{SIGBOVIK_2023_paper_23.pdf}
	{0cm}
	{}
\addpaper
	{Rizz Is All You Need: Expert Dating via Reinforcement Learning}
	{Fan Pu Zeng}
	{}
	{SIGBOVIK_2023_paper_65.pdf}
	{0cm}
	{}

\addtrack{L}{Hunger, Meet Pickle}
\addpaper
	{The Influence of Lunch Items on Cryptocurrency in the United States}
	{\protect {*David An [0x7e7]}}
	{}
	{SIGBOVIK_2023_paper_7.pdf}
	{0cm}
	{}
\addpaper
	{}
	{}
	{}
	{SIGBOVIK_2023_paper_41.pdf}
	{0cm}
	{}
\addpaper
	{Tactical Toast Cut Silhouette Recognition Guide}
	{Jim McCann}
	{}
	{SIGBOVIK_2023_paper_62.pdf}
	{0cm}
	{}
\addpaper
	{Saltgurken: A formal grammar for unambiguous grocery shopping}
	{*Eleftheria Chatziargyriou}
	{}
	{SIGBOVIK_2023_paper_34.pdf}
	{0cm}
	{}

\addtrack{M}{Hear, Meet And Now}
\addpaper
	{VOACaloid: A ``better'' ``hardware-based'' ``portable'' ``solution'' for the ``real-time'' ``generation'' of ``singing''}
	{Aaron Thapa}
	{}
	{SIGBOVIK_2023_paper_38.pdf}
	{0cm}
	{}
\addpaper
	{Avantgarde Visual Auditive JSON Hashing}
	{Tobias Coq, Louis Erhard, Julio Esperantò, Jean Parler, and Peter-Ludwig Sechsdiener}
	{}
	{SIGBOVIK_2023_paper_48.pdf}
	{0cm}
	{}

\addtrack{N}{Reader, Meet Remainder}
%withdrawn:
%\addpaper
%	{Estimating the Probability That the Explosion of an Ink Sphere Produces a Dictionary}
%	{Braden Oh}
%	{}
%	{papers/SIGBOVIK_2023_paper_1.pdf}
%	{0cm}
%	{}
\addpaper
	{New Advancements in How Fucked You Are if You Don’t Use Our Software}
	{\protect{Lemma Brummel and Society for Creating Amplified Monetizability in Augmented Industries [0x202b]}}
	{}
	{SIGBOVIK_2023_paper_25.pdf}
	{0cm}
	{}
\addpaper
	{A Retrospective Psychological Evaluation of the Logical Contradictions in Writing Systems Containing Japanese Kanji and Chinese Characters}
	{Ashvin Ranjan}
	{}
	{SIGBOVIK_2023_paper_53.pdf}
	{0cm}
	{}
\addpaper
	{Health Code: COVID Control and Advancements in Digital Image Compression}
	{Tianjian Hu}
	{}
	{SIGBOVIK_2023_paper_5.pdf}
	{0cm}
	{}
